%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Onat Dogan Akca} \\ \vspace{1pt}
    \small 123-456-7890 $|$ \href{mailto:x@x.com}{\underline{onatakca@gmail.com}} $|$ 
    \href{https://linkedin.com/in/...}{\underline{linkedin.com/in/onatakca}} $|$
    \href{https://github.com/...}{\underline{github.com/onatakca}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Twente}{Enschede, Netherlands}
      {Master of Science in Computer Science}{Aug. 2024 -- Present}
      \resumeItemListStart
        \resumeItem{\textbf{Focus of Study}: Data Science and Machine Learning}
      \resumeItemListEnd
    \resumeSubheading
      {University of Illinois Urbana-Champaign}{Champaign, IL}
      {Bachelor of Science in Computer Science}{Aug. 2019 -- May 2023}
  \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, C++, SQL, Java, C, Bash} \\
     \textbf{Machine Learning}{: PyTorch, TensorFlow, Keras, Scikit-learn, Pandas, NumPy, OpenCV, Hugging Face} \\
     \textbf{MLOps \& Cloud}{: Docker, Git, Google Cloud Platform (GCP), Weights \& Biases, Linux} \\
     \textbf{Concepts}{: Computer Vision, Deep Learning, Image Segmentation, Big Data Analytics}
    }}
 \end{itemize}
 
%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Graduate Research Assistant (Computer Vision)}{Oct 2023 -- Present}
      {Middle East Technical University (METU)}{Ankara, Turkey}
      \resumeItemListStart
        \resumeItem{Optimized \textbf{nnUNetv2} and \textbf{DeepLabv3} architectures for advanced eyelid gland segmentation, fine-tuning hyperparameters to maximize image analysis efficiency.}
        \resumeItem{Achieved a \textbf{DICE score of 0.84} for gland segmentation and \textbf{0.92} for eyelid segmentation, significantly surpassing existing benchmarks.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Engineer Intern}{June 2022 -- Aug. 2022}
      {OpenProcessing.org}{New York, NY (Remote)}
      \resumeItemListStart
        \resumeItem{Engineered a collaborative filtering recommendation system using \textbf{Python} (Pandas, NumPy) to personalize content for a user base of \textbf{100,000+ monthly users}.}
        \resumeItem{Authored technical documentation and interactive tutorials for \textbf{p5.js}, facilitating user onboarding for multiplayer game development.}
      \resumeItemListEnd

    \resumeSubheading
      {Research Assistant (Deep Learning)}{May 2022 -- Aug. 2022}
      {University of Illinois Chicago}{Chicago, IL}
      \resumeItemListStart
        \resumeItem{Designed deep neural networks in \textbf{TensorFlow} and \textbf{Keras} to analyze crash survivor datasets, automating the extraction of survival patterns from raw sensor data.}
        \resumeItem{Built automated data preprocessing pipelines in Python to clean and normalize raw datasets, ensuring compatibility with neural network architectures.}
      \resumeItemListEnd

    \resumeSubheading
      {Android Developer Intern}{June 2021 -- Aug. 2021}
      {Cybersoft}{Ankara, Turkey}
      \resumeItemListStart
        \resumeItem{Implemented in-app voice search functionality using Android Speech-to-Text, enabling hands-free song queries.}
        \resumeItem{Integrated \textbf{Spotify Web APIs} to develop a dynamic music streaming application with real-time playback control.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Project Name 1} $|$ \emph{Tech Stack (e.g. Python, PyTorch, React)}}{Date -- Date}
          \resumeItemListStart
            \resumeItem{Developed an [AI/ML Model or App] that solves [Specific Problem], achieving [Metric/Result].}
            \resumeItem{Implemented [Specific Algorithm/Technique] to optimize performance, reducing processing time by X\%.}
            \resumeItem{Deployed the model using [Docker/FastAPI/GCP], making it accessible via a web interface.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Project Name 2} $|$ \emph{Tech Stack (e.g. C++, OpenGL, SQL)}}{Date -- Date}
          \resumeItemListStart
            \resumeItem{Engineered a [System Type] capable of handling [Scale of Data/Users] with real-time updates.}
            \resumeItem{Designed a custom algorithm for [Feature], improving accuracy over standard libraries.}
            \resumeItem{View full source code and documentation at \textbf{onatda2.github.io}}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

\end{document}
